Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-06 p2/axiom-proof.tex
Clarifying inpedendence
Proof for combining independent commands

\begin{proof}
We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
Since the values in the resulting filesystems are the same,
this is only possible if, for an initial non-broken filesystem $\FS$,
one side results in a broken filesystem, and the other side does not.
Without loss of generality, we can assume
$(\cxynv\cc\czwmv)\aFS$ is not broken, but $(\czwmv\cc\cxynv)\aFS$ is.
This means that either $\czwmv\aFS$ is already broken, or it is not, and applying $\cxynv$
breaks the filesystem.

@@

\begin{proof}
It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
(they do not break the filesystem), they are equivalent.
What remains to show is that they break the same set of filesystems.
If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
and therefore $\cxwnv$ does not break $\FS$.
Conversely, if $\cxwnv$ does not break $\FS$, then 
we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
Also, as
either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
there must be a directory at $\FS(\parentf{n})$,
and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
as any value is permissible at $n$.
This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.
\end{proof}

>>>>

\begin{proof}
This proof is similar to the first case in the proof of \cref{combine_independent_commands}.
However, this result is needed for \cref{independent_details} on which that proof rests.

We use an inverse proof and assume $\cxynv\cc\czwmv \nequiv \czwmv\cc\cxynv$.
Since the values in the resulting filesystems are the same,
this is only possible if, for an initial non-broken filesystem $\FS$,
one side results in a broken filesystem, and the other side does not.
Without loss of generality, we can assume
$(\cxynv\cc\czwmv)\aFS$ is not broken, but $(\czwmv\cc\cxynv)\aFS$ is.
This means that either $\czwmv\aFS$ is already broken, or it is not, and applying $\cxynv$
breaks the filesystem.

@@

\begin{proof}
It is easy to see that where both $\cxynv\cc \czwnv$ and $\cxwnv$ are defined
(they do not break the filesystem), they are equivalent.
What remains to show is that they break the same set of filesystems.
If $(\cxynv\cc \czwnv)\aFS$ is not broken, then we know that neither of
$\FS$, $\fsreplacement{\FS}{n}{y}$ or $\fsreplacement{\FS}{n}{w}$ is broken,
and therefore $\cxwnv$ does not break $\FS$.
Conversely, if $\cxwnv$ does not break $\FS$, then 
we know that $\FS$ and $\fsreplacement{\FS}{n}{w}$ are not broken.
Also, as
either $[x]\neq[\empt]$ or $[w]\neq[\empt]$,
there must be a directory at $\FS(\parentf{n})$,
and so $\fsreplacement{\FS}{n}{y}$ cannot be broken, either,
as any value is permissible at $n$.
This is equivalent to saying that $\cxynv\cc \czwnv$ does not break the filesystem.

We note that if $\cxwnv$ is an assertion command, then it extends $\cxynv\cc\czwnv$
instead of being equivalent to it.
\end{proof}

### 2018-07-06 p2/works-inverse.tex
Proof for combining independent commands

The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.

TODO CONTINUE

Using an inverse proof we assume that for a filesystem $\FS$
both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
We know a command breaks a filesystem either if
its input type is not compatible with the filesystem,
or if the filesystem ceases to have the tree property.

We also know that whether a filesystem has the tree property
depends

The second case is that the two commands are the same and are assertion or replacement
commands, when the proposition is trivially true.
Finally, the third case is that the two commands are on comparable nodes and one of them
is an assertion command, when the proposition is again trivially true.

TODO END

Let $\alpha=\cxynv$ and $\beta=\czwmv$.
The proof is by contradiction;
assume that there is a filesystem $\FS$ for which
$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
$(\cxynv\cc \czwmv)\aFS=\fsbroken$.
We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.

We note that as the two commands are independent, they commute, and so
the proposition is symmetric.
Therefore, if either of the commands is an assertion command,
without loss of generality we can assume $\cxynv$ is an assertion command.
If so, 
$[\cxynv\aFS(m)]=[\FS(m)]$ even if $n=m$.
This means $\czwmv$ cannot break $\cxynv\aFS(m)$, which is a contradiction.

In the remaining cases neither command is an assertion command.

Applying a command can only result in a broken filesystem in two cases.
First, if the input type does not match the filesystem,
but we know $[\FS(m)]=[w]$ and so
$[\cxynv\aFS(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
Second, if the new filesystem violates the tree property.
This again cannot be the case because we also know that $n\unrel m$
and the tree property only depends on the types of values at the parent and children of $m$,
which therefore cannot be changed by $\cxynv$.
\end{proof}

>>>>

The first case is that $n\unrel m$ where $\alpha=\cxynv$, $\beta=\czwmv$.
Using an inverse proof we assume that for a filesystem $\FS$
both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, but $(\cxynv\cc\czwmv)\FS$ is broken.
Since $n\neq m$, we know the input types of the command are compatible with $\FS$,
so $\FS$ must be broken because it violates the tree property.

We know that applying $\czwmv$ breaks $\cxynv\aFS$. As it changes the filesystem
at $m$, this can be because either $m$ would no longer be a directory but has non-empty children,
or $\parentf{m}$ is not a directory but acquired non-empty children.
Let us look at the first case.
Since $n\indep m$, we know the parent and children of $m$ have the same value
in $\FS$ as in $\cxynv\aFS$. However, this leads to contradiction
as applying $\czwmv$ to $\cxynv\aFS$ leads to a broken filesystem, but
applying it to $\FS$ does not.

Therefore $\parentf{m}$ must not be a directory in $\FS$ but acquire non-empty children.
Since $\czwmv\aFS$ is defined, it must be $\cxynv$ that changes the children of
$\parentf{m}$ in this way, which means that $n$ and $m$ must be siblings.
As then the value at $\parentf{n}=\parentf{m}$ is not changed by either command,
we know it cannot be a directory in $\FS$, either, and that therefore
$\FS$ is empty at all children of the parent node.
This means that $[x]=[z]=[\empt]$, and
since both $\cxynv\aFS$ and $\czwmv\aFS$ are defined, $y=w=\empt$ must also hold.
However, this contradicts our assumption that $(\cxynv\cc\czwmv)\FS$ is broken.

The second case is that the two commands are the same and are assertion or replacement
commands, when the proposition is trivially true.
Finally, the third case is that the two commands are on comparable nodes and one of them
is an assertion command, when the proposition is again trivially true.
\end{proof}
